Modeling the Linux page cache for accurate simulation of data-intensive applications

### 2021-05-21 paper_io_sim.tex
Update cache eviction simulation, WRENCH commmit used

    The cache eviction simulation also runs in
    the main thread. It frees up the page cache by traversing and deleting
    least recently used clean data blocks in the inactive list.
    The amount of data to evict is passed as a parameter and data blocks are deleted
    from the inactive list until the evicted data reaches the required amount,
    or until there is no clean block left in the list.
    If the last evicted block does not have to be entirely evicted, the block is split into two blocks,
    and only one of them is evicted.
    The overhead of the cache eviction algorithm is not part of the simulated time
    since cache eviction time is negligible in real systems. % \tristan{a reference would be welcome}.

@@

            We also implemented our model as part of \wrench, enhancing its
            internal implementation and APIs with a page cache abstraction,
            and allowing users to activate the feature via a command-line
            argument. We used SimGrid's locking mechanism to handle
            concurrent accesses to page cache LRU lists by the two Memory
            Manager threads. For the experiments, we used
            \wrench 1.6 at commit
            \href{https://github.com/wrench-project/wrench/tree/67185374330d2c4bf274fce222c937e838df5b03}{6718537433},
            which uses \simgrid 3.25, available at
            \url{https://framagit.org/simgrid/simgrid}. Our implementation
            is now part of \wrench's master branch and available to
            users in the 1.8 release. \wrench provides a full \simgrid-based simulation 
            environment that supports, among other features, concurrent accesses to storage devices, 
            applications distributed on multiple hosts, network transfers, 
            and multi-threading.

>>>>

    The cache eviction simulation also runs in
    the main thread. It frees up the page cache by traversing and deleting
    least recently used clean data blocks in the inactive list.
    In case the amount evictable memory in the inactive list is insufficient 
    (the inactive list is empty or a file being opened is residing in the inactive list), 
    blocks in the active list are considered for eviction. 
    The amount of data to evict is passed as a parameter and data blocks are deleted
    from the lists until the evicted data reaches the required amount,
    or until there is no clean block left in the list.
    If the last evicted block does not have to be entirely evicted, the block is split into two blocks,
    and only one of them is evicted.
    The overhead of the cache eviction algorithm is not part of the simulated time
    since cache eviction time is negligible in real systems. % \tristan{a reference would be welcome}.

@@

            We also implemented our model as part of \wrench, enhancing its
            internal implementation and APIs with a page cache abstraction,
            and allowing users to activate the feature via a command-line
            argument. We used SimGrid's locking mechanism to handle
            concurrent accesses to page cache LRU lists by the two Memory
            Manager threads. For the experiments, we used
            \wrench 1.6 at commit
            \href{https://github.com/dohoangdzung/wrench/tree/cefc0bf739d015b2329a62750a9d70085b65a3ae}{cefc0bf739},
            which uses \simgrid 3.26, available at
            \url{https://framagit.org/simgrid/simgrid}. Our implementation
            is now part of \wrench's master branch and available to
            users in the 1.8 release. \wrench provides a full \simgrid-based simulation 
            environment that supports, among other features, concurrent accesses to storage devices, 
            applications distributed on multiple hosts, network transfers, 
            and multi-threading.
